---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

### Importing the libraries, data & setting WD

```{r}
library(dplyr)
library(stringr)
library(tidyr)
setwd("C:/Users/Emma/Desktop/Enron")
emails=read.csv("emails.csv",nrows=1000, stringsAsFactors = F)
```
```{r eval=T}
#head(emails,1)
emails[1,]
```
### Extracting the data 

At the moment, the data is in an unstructured format.  The first thing that needs to be done, is to extract data from the different components of the email.

#### Step 1:
Split the data into the headings and body of the email:

```{r}
#splitting the data by the strt of the email tag tag \n\n
#splits data into message
email_text=as.data.frame(str_split_fixed(emails$message, "\n\n", 2))
names(email_text)=c("Headings", "Body")
```

#### Step 2:
Split the Headings section into more sensible columns, for analysis purposes:
```{r}
Messageid=(str_sub(str_extract(email_text$Headings,"Message-ID:.*"),start=12))
Date=(str_sub(str_extract(email_text$Headings,"Date:.*"),start=7))
From=(str_sub(str_extract(email_text$Headings,"From:.*"),start=7))
To=(str_sub(str_extract(email_text$Headings,"To:.*"),start=5))
Subject=(str_sub(str_extract(email_text$Headings,"Subject:.*"),start=10))
Mimeversion=(str_sub(str_extract(email_text$Headings,"Mime-Version:.*"),start=15))
Contenttype=(str_sub(str_extract(email_text$Headings,"Content-Type:.*"),start=15))
Contentencoding=(str_sub(str_extract(email_text$Headings,"Content-Transfer-Encoding:.*"),start=28))
cc=(str_sub(str_extract(email_text$Headings,"X-cc:.*"),start=7))
bcc=(str_sub(str_extract(email_text$Headings,"X-bcc:.*"),start=8))
Folder=(str_sub(str_extract(email_text$Headings,"X-Folder:.*"),start=11))
origin=(str_sub(str_extract(email_text$Headings,"X-Origin:.*"),start=11))
filename=(str_sub(str_extract(email_text$Headings,"X-FileName:.*"),start=12))

emails_split=data.frame(Messageid,Date,From,To,Subject,Mimeversion,Contentencoding,Contenttype,cc,bcc,Folder,origin, filename,email_text$Body,stringsAsFactors=FALSE)

```

Now the data is in a more human readable format.

```{r}
emails_split[2,]

```