---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

### Importing the libraries, data & setting WD

```{r}
library(dplyr)
library(stringr)
library(tidyr)
library(stargazer)
library(xtable)
library(data.table)
setwd("C:/Users/Emma/Desktop/Enron")
emails=read.csv("emails.csv",nrows=1000, stringsAsFactors = F)
```
```{r eval=T}
#head(emails,1)
emails[1,]
```
### Extracting the data 

At the moment, the data is in an unstructured format.  The first thing that needs to be done, is to extract data from the different components of the email.

#### Step 1:
Split the data into the headings and body of the email:

```{r}
#splitting the data by the strt of the email tag tag \n\n
#splits data into message
email_text=as.data.frame(str_split_fixed(emails$message, "\n\n", 2))
names(email_text)=c("Headings", "Body")
```

#### Step 2:
Split the Headings section into more sensible columns, for analysis purposes:
```{r}
Messageid=(str_sub(str_extract(email_text$Headings,"Message-ID:.*"),start=12))
Date=(str_sub(str_extract(email_text$Headings,"Date:.*"),start=7))
From=(str_sub(str_extract(email_text$Headings,"From:.*"),start=7))
To=(str_sub(str_extract(email_text$Headings,"To:.*"),start=5))
Subject=(str_sub(str_extract(email_text$Headings,"Subject:.*"),start=10))
Mimeversion=(str_sub(str_extract(email_text$Headings,"Mime-Version:.*"),start=15))
Contenttype=(str_sub(str_extract(email_text$Headings,"Content-Type:.*"),start=15))
Contentencoding=(str_sub(str_extract(email_text$Headings,"Content-Transfer-Encoding:.*"),start=28))
cc=(str_sub(str_extract(email_text$Headings,"X-cc:.*"),start=7))
bcc=(str_sub(str_extract(email_text$Headings,"X-bcc:.*"),start=8))
Folder=(str_sub(str_extract(email_text$Headings,"X-Folder:.*"),start=11))
origin=(str_sub(str_extract(email_text$Headings,"X-Origin:.*"),start=11))
filename=(str_sub(str_extract(email_text$Headings,"X-FileName:.*"),start=12))

emails_split=data.frame(Messageid,Date,From,To,Subject,Mimeversion,Contentencoding,Contenttype,cc,bcc,Folder,origin, filename,email_text$Body,stringsAsFactors=FALSE)

```

Now the data is in a more human readable format.Here is what the first row of data looks like:

```{r}
data.table(emails_split[1,])
```

But this isn't very easy to read, so let's create a new table with information such as date, from, to and message. 

```{r}
email_content=data.frame(emails_split$Date,emails_split$From,emails_split$To,emails_split$email_text.Body)
names(email_content)=c("Date","From","To","Body")
head(email_content)
```
Let's also tidy up the date timestamps so we do some analysis on these.  Firsly, we need to convert the Date column into actual date format in R:

```{r}
str(email_content) #not in date format yet, so need to convert this
library(lubridate)

email_content=email_content%>%
  mutate(Date_formatted=as.POSIXct(Date,format="%a, %d %b %Y %H:%M:%S %z"))

attributes(email_content$Date_formatted)$tzone = "America/Los_Angeles"

email_content=email_content%>%
  mutate(year=year(Date_formatted),
         month=month(Date_formatted,label=T),mday=mday(Date_formatted),
         day=wday(Date_formatted,label=T),hour=hour(Date_formatted), 
         minute=minute(Date_formatted))

 
```

Now we can extract all the individual elements to see things like day, time, month, year etc for doing some aggregations later.




#### Who sent the most emails and to whom?



#### Most common times emails were sent


#### Topic modelling 


#### Word cloud from emails
